---
title: "Linear Regression Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linear Regression Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab4Package)
```
# Overview
This vignette illustrates how the package [Lab4Package](https://github.com/jmparlad/Lab-4.git) works and it explains its different functionalities for handling linear regression models and making a simple regression analysis. The package is built using RC Object Oriented Programming, so that after initializing a class the user can have direct access to the different regression parameters and use the different functionalities of the class in an easy way.

# Initializing the class
The first step for using the package is assigning the class. To do this, a data set and a formula or relation between the model variables should be introduced as input. This can be done as in the following example, where the well known data set iris is used:
```{r}
data(iris)
linreg_ex <- linreg$new(Petal.Length ~ Species, data = iris)
```
Once the class is initialized, the regression parameters and the class methods can be called with simple commands.

# Linear regression parameters
The following regression parameters can be accessed within the class:

* Regression coefficients $\hat{\beta}$:
```{r}
linreg_ex$regCoeff
```
* Fitted values $\hat{y}$:
```{r}
linreg_ex$y_fitted
```
* Residuals $df$:
```{r}
linreg_ex$residuals
```
* Degrees of freedom $\hat{e}$:
```{r}
linreg_ex$degrees
```
* Residual variance $\hat{\sigma}^2$:
```{r}
linreg_ex$residual_variance
```
* Variance of regression coefficients $\hat{Var}(\hat{\beta})$:
```{r}
linreg_ex$coefficient_variance
```
* t-values $t_\beta$:
```{r}
linreg_ex$t_values
```
* p-values $p_\beta$:
```{r}
linreg_ex$p_values
```

# Linear regression functions
The following functions can be used to do an analysis of the regression model:

* Print coefficients and coefficient names:
```{r}
linreg_ex$print()
```
* Plot regression graphs:
```{r}
linreg_ex$plot()
```

* Return vector of residuals $\hat{e}$:
```{r}
linreg_ex$resid()
```
* Return the predicted values $\hat{y}$:
```{r}
linreg_ex$pred()
```
* Return the coefficients as a named vector:
```{r}
linreg_ex$coef()
```
* Print a summary of the regression model:
```{r}
linreg_ex$summary()
```